Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-09 draft.tex
Added author roles
Another revision of "The ReScience initiative"

% Hyperref
\usepackage{xcolor}
\definecolor{blendedblue}{rgb}{0.2, 0.2, 0.6}
\definecolor{blendedred}{rgb}{0.8, 0.2, 0.2}
\usepackage[bookmarks=true,
            breaklinks=true,
            pdfborder={0 0 0},
            citecolor=blendedblue,
            colorlinks=true,
            linkcolor=blendedblue,
            urlcolor=blendedblue,
            citecolor=blendedblue,
            linktocpage=false,
            hyperindex=true,
            linkbordercolor=white]{hyperref}
\usepackage{hyperref}
\hypersetup{colorlinks=true}

@@

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \begin{small}
    \input{authors.tex}
  \end{small}
\begin{footnotesize}
  \vspace{2mm}
  \input{affiliations.tex}
  $^{*}$Corresponding author:
        \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}

@@

Performing a replication is a daunting task that is traditionally hardly or not
at all rewarded. Nevertheless, some people are actually willing to replicate
computational research. The motivations for doing so are very diverse (see Box 1). Students may want familiarize themselves with
a specific scientific domain, and acquire relevant practical experience by replicating important published work. Senior researchers may critically
need a specific piece of code for a research project and therefore re-implement a published computational method. If these people write a brand new
open source implementation of already published research, chances are that this new
implementation may be of great interest for other people as well, including
the original authors. The question is where to publish such a replication. To the
best of our knowledge, no major journal accepts publishing replications in computational science. This has been the main motivation for the
creation of the ReScience journal (\href{https://rescience.github.io}{rescience.github.io}) by Konrad Hinsen and Nicolas P. Rougier in September 2015.\\

@@

ReScience is an openly peer-reviewed journal that targets computational research
and encourages the explicit replication of already published research. In order
to provide the largest benefit to the scientific community, replications are
required to be reproducible and open-source. In less than two years of existence, 12
articles have been published and 3 are currently under review
(\href{https://github.com/ReScience/ReScience-submission/pull/20}{\#20},
\href{https://github.com/ReScience/ReScience-submission/pull/27}{\#27},
\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#30}). The
editorial board covers a wide range of computational sciences (see
\url{http://rescience.github.io/board/}) and more than 70 volunteers have registered to be reviewers. The computational domains of published work
are in computational neuroscience, neuroimaging, computational ecology and
computer graphics with a majority in computational neuroscience. There is a
strong bias towards successful replication (100\%) and experience has
taught us that researchers are reluctant to publish failed replications, even when they can prove that the original work is wrong. For young researchers,
there is a social/professional risk in publishing articles that show
results from a senior researcher to be wrong. Until we implement a
certified anonymized submission process, this strong bias will most likely
remain.\\

One of the specificities of the ReScience journal is its publishing
chain that is radically different from any other traditional
scientific journals since ReScience lives on GitHub. One of the
consequences is that the whole process, from submission via reviewing
to publication, is open for anyone to see and even comment on.\\

Each submission takes the form of a pull request that is first
considered by a member of the editorial board, who may decide to
reject the submission if it does not respect the formal publication
criteria of ReScience. A submission must contain
\begin{itemize}
\item a precise reference to the work being replicated,
\item an explanation of why the authors think they have replicated the paper
      (same figures, same graphics,same behavior, etc.),
\item a description of any difficulties encountered during the
      replication,
\item open-source code that produces the replication results,
\item an explanation of this code for human readers.
\end{itemize}
A complete submission therefore consists of both code and an accompanying
article. Partial replications that cover only some of the results in the
original work are acceptable, but need to be justified.\\

If the submission respects these criteria, the editor assigns it to
two reviewers for further evaluation and tests. The reviewers evaluate
the code and the accompanying material in continuous interaction with
the authors through the discussion section until both reviewers
consider the work acceptable for publication. The goal of the review
is thus to help the authors meet the ReScience quality standards
through discussion. Since ReScience targets replication of already
published work, the criteria of relevance or novelty applied by most
traditional journals are irrelevant.

For a submission to be accepted, both reviewers must consider it
reproducible and a valid replication of the original work. As we
explained in section~\ref{sec:replication-reproduction}, this means
that the reviewers
\begin{itemize}
\item are able to run the proposed implementation on their computers,
\item obtain the same results as indicated in the accompanying paper,
\item consider these results sufficiently close to the ones reported in the original paper being replicated.
\end{itemize}
%
% The review concentrates on how easy it would be for another researcher
% to run the proposed implementation. This should be viewed in light of
% the standards in the field. If a given tool/library/software is
% mainstream in a field, it is ok to use them, but if a brand new
% standalone implementation is proposed, this must not rejected on this
% criterion.

Since independent implementation is a major criterion in replication
work, ReScience does not allow authors to submit replications of their
own research, nor the research of close collaborators. Mistakes in the
implementation of computational models and methods are often due to
biases that authors invariably have, consciously or not. Such biases
will inevitably carry over to a replication. Perhaps even more
importantly, cross-fertilization is generally useful in research, and
trying to replicate the work of one’s peers might pave the way for a
future collaboration, or may give rise to new ideas as a result of the
replication effort.

>>>>

% Hyperref
\usepackage{xcolor}
\definecolor{blendedblue}{rgb}{0.2, 0.2, 0.6}
\definecolor{blendedred}{rgb}{0.8, 0.2, 0.2}
\usepackage[bookmarks=true,
            breaklinks=true,
            pdfborder={0 0 0},
            citecolor=blendedblue,
            colorlinks=true,
            linkcolor=blendedblue,
            urlcolor=blendedblue,
            citecolor=blendedblue,
            linktocpage=false,
            hyperindex=true,
            linkbordercolor=white]{hyperref}
\hypersetup{colorlinks=true}

@@

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \begin{small}
    \input{authors.tex}
  \end{small}
\begin{footnotesize}
  \vspace{2mm}
  \input{affiliations.tex}
  \vspace{2mm}
  $^{\dagger}$ReScience editor
  $^{\ddagger}$ReScience reviewer
  $^{\S}$ReScience author\\
  $^{\star}$Corresponding author:
            \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}

@@

Performing a replication is a daunting task that is traditionally not well
rewarded. Nevertheless, some people are actually willing to replicate
computational research. The motivations for doing so are very diverse (see Box 1). Students may want to familiarize themselves with
a specific scientific domain, and acquire relevant practical experience by replicating important published work. Senior researchers may critically
need a specific piece of code for a research project and therefore re-implement a published computational method. If these people write a brand new
open source implementation of already published research, chances are that this new
implementation may be of interest for other people as well, including
the original authors. The question is where to publish such a replication. To the
best of our knowledge, no major journal accepts publishing replications in computational science. This has been the main motivation for the
creation of the ReScience journal (\href{https://rescience.github.io}{rescience.github.io}) by Konrad Hinsen and Nicolas P. Rougier in September 2015.\\

@@

ReScience is an openly peer-reviewed journal that targets computational research
and encourages the explicit replication of already published research. In order
to provide the largest possible benefit to the scientific community, replications are
required to be reproducible and open-source. In less than two years of existence, 12
articles have been published and 3 are currently under review
(\href{https://github.com/ReScience/ReScience-submission/pull/20}{\#20},
\href{https://github.com/ReScience/ReScience-submission/pull/27}{\#27},
\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#30}). The
editorial board covers a wide range of computational sciences (see
\url{http://rescience.github.io/board/}) and more than 70 volunteers have registered to be reviewers. The scientific domains of published work
are computational neuroscience, neuroimaging, computational ecology and
computer graphics, with a majority in computational neuroscience. There is a
strong bias towards successful replication (100\%) and experience has
taught us that researchers are reluctant to publish failed replications, even when they can prove that the original work is wrong. For young researchers,
there is a social/professional risk in publishing articles that show
results from a senior researcher to be wrong. Until we implement a
certified anonymized submission process, this strong bias will most likely
remain.\\

One of the specificities of the ReScience journal is its publishing
chain that is radically different from any other traditional
scientific journals since ReScience lives on GitHub, a platform
originally designed for collaborative software development. A
ReScience submission is treated very similarly to a contribution to an
Open Source software project. One of the consequences is that the
whole process, from submission via reviewing
to publication, is open for anyone to see and even comment on.\\

Each submission takes the form of a pull request that is first
considered by a member of the editorial board, who may decide to
reject the submission if it does not respect the formal publication
criteria of ReScience. A submission must contain
\begin{itemize}
\item a precise reference to the work being replicated,
\item an explanation of why the authors think they have replicated the paper
      (same figures, same graphics, same behavior, etc.),
\item a description of any difficulties encountered during the
      replication,
\item open-source code that produces the replication results,
\item an explanation of this code for human readers.
\end{itemize}
A complete submission therefore consists of both code and an accompanying
article. Partial replications that cover only some of the results in the
original work are acceptable, but must be justified.\\

If the submission respects these criteria, the editor assigns it to
two reviewers for further evaluation and tests. The reviewers evaluate
the code and the accompanying material in continuous interaction with
the authors through the discussion section until both reviewers
consider the work acceptable for publication. The goal of the review
is thus to help the authors meet the ReScience quality standards
through discussion. Since ReScience targets replication of already
published work, the criteria of importance or novelty applied by most
traditional journals are irrelevant.

For a submission to be accepted, both reviewers must consider it
reproducible and a valid replication of the original work. As we
explained earlier, this means that the reviewers
\begin{itemize}
\item are able to run the proposed implementation on their computers,
\item obtain the same results as indicated in the accompanying paper,
\item consider these results sufficiently close to the ones reported in the original paper being replicated.
\end{itemize}
%
% The review concentrates on how easy it would be for another researcher
% to run the proposed implementation. This should be viewed in light of
% the standards in the field. If a given tool/library/software is
% mainstream in a field, it is ok to use them, but if a brand new
% standalone implementation is proposed, this must not rejected on this
% criterion.

Since independent implementation is a major feature of replication
work, ReScience does not allow authors to submit replications of their
own research, nor the research of close collaborators. Mistakes in the
implementation of computational models and methods are often due to
biases that authors invariably have, consciously or not. Such biases
will inevitably carry over to a replication. Perhaps even more
importantly, cross-fertilization is generally useful in research, and
trying to replicate the work of one’s peers might pave the way for a
future collaboration, or may give rise to new ideas as a result of the
replication effort.
